{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Models for detecting BHBH, BHNS and NSNS binaries with LISA

### 2021-11-16 paper/tex/sections/appendix.tex
reduce sig figs

        A & fiducial & \confinv{124.3}{11.3}{10.7} & \confinv{74.0}{9.0}{9.0} & \confinv{42.4}{6.4}{6.6} & \confinv{7.9}{2.9}{3.1} & \confinv{202.2}{14.2}{13.8} & \confinv{117.9}{10.9}{11.1} & \confinv{71.3}{8.3}{8.7} & \confinv{13.0}{4.0}{4.0}\\
        B & $\beta=0.25$ & \confinv{94.1}{10.1}{9.9} & \confinv{68.8}{7.8}{8.2} & \confinv{22.4}{4.4}{4.6} & \confinv{2.9}{1.9}{2.1} & \confinv{149.3}{12.3}{12.7} & \confinv{107.8}{10.8}{10.2} & \confinv{36.9}{5.9}{6.1} & \confinv{4.6}{1.6}{2.4}\\
        C & $\beta=0.5$ & \confinv{59.2}{8.2}{7.8} & \confinv{47.0}{7.0}{7.0} & \confinv{8.3}{3.3}{2.7} & \confinv{3.9}{1.9}{2.1} & \confinv{95.9}{9.9}{10.1} & \confinv{75.8}{8.8}{9.2} & \confinv{13.6}{3.6}{3.4} & \confinv{6.4}{2.4}{2.6}\\
        D & $\beta=0.75$ & \confinv{67.0}{8.0}{8.0} & \confinv{46.9}{6.9}{7.1} & \confinv{7.4}{2.4}{2.6} & \confinv{12.7}{3.7}{3.3} & \confinv{104.5}{10.5}{10.5} & \confinv{71.2}{8.2}{8.8} & \confinv{12.1}{3.1}{3.9} & \confinv{21.1}{4.1}{4.9}\\
        E & no case BB & \confinv{76.7}{8.7}{8.3} & \confinv{69.3}{8.3}{8.7} & \confinv{7.3}{2.3}{2.7} & \boldconfinv{0.2}{0.2}{0.8} & \confinv{121.4}{11.4}{10.6} & \confinv{109.3}{10.3}{10.7} & \confinv{11.8}{3.8}{3.2} & \boldconfinv{0.4}{0.4}{0.6}\\
        F & E + K & \boldconfinv{320.9}{17.9}{18.1} & \boldconfinv{154.3}{12.3}{12.7} & \boldconfinv{148.4}{12.4}{12.6} & \confinv{18.2}{4.2}{3.8} & \boldconfinv{483.7}{21.7}{22.3} & \boldconfinv{239.5}{15.5}{15.5} & \confinv{216.8}{14.8}{15.2} & \confinv{27.4}{5.4}{5.6}\\
        G & $\alpha_{\rm CE}=0.1$ & \confinv{40.2}{6.2}{6.8} & \confinv{27.9}{4.9}{5.1} & \boldconfinv{2.1}{1.1}{1.9} & \confinv{10.2}{3.2}{2.8} & \confinv{64.1}{8.1}{7.9} & \confinv{43.9}{6.9}{7.1} & \boldconfinv{3.5}{1.5}{1.5} & \confinv{16.7}{3.7}{4.3}\\
        H & $\alpha_{\rm CE}=0.5$ & \confinv{85.9}{8.9}{9.1} & \confinv{58.3}{7.3}{7.7} & \confinv{21.8}{4.8}{4.2} & \confinv{5.9}{2.9}{2.1} & \confinv{136.2}{11.2}{11.8} & \confinv{91.6}{9.6}{9.4} & \confinv{34.9}{5.9}{6.1} & \confinv{9.7}{2.7}{3.3}\\
        I & $\alpha_{\rm CE}=2.0$ & \confinv{133.3}{11.3}{11.7} & \confinv{67.6}{8.6}{8.4} & \confinv{38.0}{6.0}{6.0} & \confinv{27.7}{5.7}{5.3} & \confinv{218.4}{14.4}{14.6} & \confinv{109.6}{10.6}{10.4} & \confinv{62.7}{7.7}{8.3} & \confinv{46.0}{7.0}{7.0}\\
        J & $\alpha_{\rm CE}=10.0$ & \confinv{77.9}{8.9}{9.1} & \confinv{26.7}{4.7}{5.3} & \confinv{16.3}{4.3}{3.7} & \boldconfinv{34.9}{5.9}{6.1} & \confinv{126.2}{11.2}{10.8} & \confinv{42.4}{6.4}{6.6} & \confinv{26.6}{5.6}{5.4} & \boldconfinv{57.2}{7.2}{7.8}\\
        K & optimistic
        CE & \confinv{218.3}{15.3}{14.7} & \confinv{151.5}{12.5}{12.5} & \confinv{56.8}{7.8}{7.2} & \confinv{9.9}{2.9}{3.1} & \confinv{341.5}{18.5}{18.5} & \confinv{229.7}{14.7}{15.3} & \confinv{96.1}{10.1}{9.9} & \confinv{15.8}{3.8}{4.2}\\
        L & rapid SN & \confinv{127.3}{11.3}{11.7} & \confinv{50.4}{7.4}{6.6} & \confinv{70.2}{8.2}{8.8} & \confinv{6.7}{2.7}{2.3} & \confinv{204.9}{13.9}{14.1} & \confinv{76.6}{8.6}{8.4} & \confinv{117.4}{10.4}{10.6} & \confinv{10.8}{2.8}{3.2}\\
        M & max $m_{\rm NS}$
        $2.0 \, {\rm M_{\odot}}$ & \confinv{133.5}{11.5}{11.5} & \confinv{96.2}{10.2}{9.8} & \confinv{30.1}{5.1}{5.9} & \confinv{7.2}{2.2}{2.8} & \confinv{215.2}{14.2}{14.8} & \confinv{153.7}{12.7}{12.3} & \confinv{49.9}{6.9}{7.1} & \confinv{11.6}{3.6}{3.4}\\
        N & max $m_{\rm NS}$
        $3.0 \, {\rm M_{\odot}}$ & \confinv{118.4}{10.4}{10.6} & \confinv{58.3}{7.3}{7.7} & \confinv{51.9}{6.9}{7.1} & \confinv{8.2}{3.2}{2.8} & \confinv{189.9}{13.9}{14.1} & \confinv{91.6}{9.6}{9.4} & \confinv{84.8}{8.8}{9.2} & \confinv{13.5}{3.5}{3.5}\\
        O & no PISN & \confinv{126.7}{11.7}{11.3} & \confinv{75.3}{8.3}{8.7} & \confinv{43.4}{6.4}{6.6} & \confinv{8.0}{3.0}{3.0} & \confinv{205.7}{14.7}{14.3} & \confinv{120.5}{10.5}{10.5} & \confinv{72.3}{8.3}{8.7} & \confinv{12.8}{3.8}{3.2}\\
        P & $\sigma_{\rm cc}$
        $100 \, {\rm km s^{-1}}$ & \confinv{184.6}{13.6}{13.4} & \confinv{82.7}{8.7}{9.3} & \confinv{86.6}{9.6}{9.4} & \confinv{15.4}{4.4}{3.6} & \confinv{300.8}{17.8}{17.2} & \confinv{130.1}{11.1}{11.9} & \confinv{145.1}{12.1}{11.9} & \confinv{25.6}{4.6}{5.4}\\
        Q & $\sigma_{\rm cc}$
        $30 \, {\rm km s^{-1}}$ & \confinv{268.3}{16.3}{16.7} & \confinv{91.8}{9.8}{9.2} & \confinv{142.9}{11.9}{12.1} & \confinv{33.6}{5.6}{5.4} & \confinv{426.8}{20.8}{21.2} & \confinv{142.9}{11.9}{12.1} & \boldconfinv{229.0}{15.0}{15.0} & \confinv{54.9}{7.9}{7.1}\\
        R & no BH
        kicks & \confinv{230.2}{15.2}{14.8} & \confinv{90.8}{9.8}{9.2} & \confinv{132.1}{11.1}{11.9} & \confinv{7.2}{2.2}{2.8} & \confinv{372.7}{19.7}{19.3} & \confinv{142.3}{12.3}{11.7} & \confinv{218.6}{14.6}{14.4} & \confinv{11.8}{3.8}{3.2}\\
        S & $f_{\rm WR} = 0.1$ & \confinv{118.5}{10.5}{10.5} & \confinv{75.7}{8.7}{8.3} & \confinv{34.0}{6.0}{6.0} & \confinv{8.8}{2.8}{3.2} & \confinv{182.5}{13.5}{13.5} & \confinv{112.4}{10.4}{10.6} & \confinv{55.8}{7.8}{7.2} & \confinv{14.3}{4.3}{3.7}\\
        T & $f_{\rm WR} = 5$ & \boldconfinv{29.7}{5.7}{5.3} & \boldconfinv{5.7}{2.7}{2.3} & \confinv{15.5}{3.5}{3.5} & \confinv{8.5}{2.5}{2.5} & \boldconfinv{48.8}{6.8}{7.2} & \boldconfinv{9.2}{3.2}{2.8} & \confinv{26.2}{5.2}{4.8} & \confinv{13.4}{3.4}{3.6}\\

@@

        - & Minimum rate & \confinv{29.7}{5.7}{5.3} & \confinv{5.7}{2.7}{2.3} & \confinv{2.1}{1.1}{1.9} & \confinv{0.2}{0.2}{0.8} & \confinv{48.8}{6.8}{7.2} & \confinv{9.2}{3.2}{2.8} & \confinv{3.5}{1.5}{1.5} & \confinv{0.4}{0.4}{0.6} \\
        - & Maximum rate & \confinv{320.9}{17.9}{18.1} & \confinv{154.3}{12.3}{12.7} & \confinv{148.4}{12.4}{12.6} & \confinv{34.9}{5.9}{6.1} & \confinv{483.7}{21.7}{22.3} & \confinv{239.5}{15.5}{15.5} & \confinv{229.0}{15.0}{15.0} & \confinv{57.2}{7.2}{7.8} \\

>>>>

        A & Fiducial & \confinv{124}{11}{11} & \confinv{74}{9}{9} & \confinv{42}{6}{7} & \confinv{8}{3}{3} & \confinv{202}{14}{14} & \confinv{118}{11}{11} & \confinv{71}{8}{9} & \confinv{13}{4}{4}\\
        B & Fixed mass transfer efficiency of $\beta=0.25$ & \confinv{94}{10}{10} & \confinv{69}{8}{8} & \confinv{22}{4}{5} & \confinv{3}{2}{2} & \confinv{149}{12}{13} & \confinv{108}{11}{10} & \confinv{37}{6}{6} & \confinv{5}{2}{2}\\
        C & Fixed mass transfer efficiency of $\beta=0.5$ & \confinv{59}{8}{8} & \confinv{47}{7}{7} & \confinv{8}{3}{3} & \confinv{4}{2}{2} & \confinv{96}{10}{10} & \confinv{76}{9}{9} & \confinv{14}{4}{3} & \confinv{6}{2}{3}\\
        D & Fixed mass transfer efficiency of $\beta=0.75$ & \confinv{67}{8}{8} & \confinv{47}{7}{7} & \confinv{7}{2}{3} & \confinv{13}{4}{3} & \confinv{104}{10}{11} & \confinv{71}{8}{9} & \confinv{12}{3}{4} & \confinv{21}{4}{5}\\
        E & No Case BB mass transfer systems & \confinv{77}{9}{8} & \confinv{69}{8}{9} & \confinv{7}{2}{3} & \confinv{0}{0}{1} & \confinv{121}{11}{11} & \confinv{109}{10}{11} & \confinv{12}{4}{3} & \confinv{0}{0}{1}\\
        F & Case BB Unstable + Optimistic CE & \confinv{321}{18}{18} & \confinv{154}{12}{13} & \confinv{148}{12}{13} & \confinv{18}{4}{4} & \confinv{484}{22}{22} & \confinv{240}{16}{15} & \confinv{217}{15}{15} & \confinv{27}{5}{6}\\
        G & CE efficiency $\alpha = 0.1$ & \confinv{40}{6}{7} & \confinv{28}{5}{5} & \confinv{2}{1}{2} & \confinv{10}{3}{3} & \confinv{64}{8}{8} & \confinv{44}{7}{7} & \confinv{3}{1}{2} & \confinv{17}{4}{4}\\
        H & CE efficiency $\alpha = 0.5$ & \confinv{86}{9}{9} & \confinv{58}{7}{8} & \confinv{22}{5}{4} & \confinv{6}{3}{2} & \confinv{136}{11}{12} & \confinv{92}{10}{9} & \confinv{35}{6}{6} & \confinv{10}{3}{3}\\
        I & CE efficiency $\alpha = 2.0$ & \confinv{133}{11}{12} & \confinv{68}{9}{8} & \confinv{38}{6}{6} & \confinv{28}{6}{5} & \confinv{218}{14}{15} & \confinv{110}{11}{10} & \confinv{63}{8}{8} & \confinv{46}{7}{7}\\
        J & CE efficiency $\alpha = 10.0$ & \confinv{78}{9}{9} & \confinv{27}{5}{5} & \confinv{16}{4}{4} & \confinv{35}{6}{6} & \confinv{126}{11}{11} & \confinv{42}{6}{7} & \confinv{27}{6}{5} & \confinv{57}{7}{8}\\
        K & HG donor stars initiating a CE survive CE & \confinv{218}{15}{15} & \confinv{152}{13}{12} & \confinv{57}{8}{7} & \confinv{10}{3}{3} & \confinv{341}{18}{19} & \confinv{230}{15}{15} & \confinv{96}{10}{10} & \confinv{16}{4}{4}\\
        L & Fryer rapid SN remnant mass prescription & \confinv{127}{11}{12} & \confinv{50}{7}{7} & \confinv{70}{8}{9} & \confinv{7}{3}{2} & \confinv{205}{14}{14} & \confinv{77}{9}{8} & \confinv{117}{10}{11} & \confinv{11}{3}{3}\\
        M & Maximum NS mass = 2.0 ${\rm M_{\odot}}$ & \confinv{133}{11}{12} & \confinv{96}{10}{10} & \confinv{30}{5}{6} & \confinv{7}{2}{3} & \confinv{215}{14}{15} & \confinv{154}{13}{12} & \confinv{50}{7}{7} & \confinv{12}{4}{3}\\
        N & Maximum NS mass = 3.0 ${\rm M_{\odot}}$ & \confinv{118}{10}{11} & \confinv{58}{7}{8} & \confinv{52}{7}{7} & \confinv{8}{3}{3} & \confinv{190}{14}{14} & \confinv{92}{10}{9} & \confinv{85}{9}{9} & \confinv{13}{3}{4}\\
        O & No PISN and pulsational-PISN & \confinv{127}{12}{11} & \confinv{75}{8}{9} & \confinv{43}{6}{7} & \confinv{8}{3}{3} & \confinv{206}{15}{14} & \confinv{121}{11}{10} & \confinv{72}{8}{9} & \confinv{13}{4}{3}\\
        P & $\sigma_{\rm RMS}^{\rm 1D} = 100 \ {\rm km\ s^{-1}}$ for CCSN & \confinv{185}{14}{13} & \confinv{83}{9}{9} & \confinv{87}{10}{9} & \confinv{15}{4}{4} & \confinv{301}{18}{17} & \confinv{130}{11}{12} & \confinv{145}{12}{12} & \confinv{26}{5}{5}\\
        Q & $\sigma_{\rm RMS}^{\rm 1D} = 30 \ {\rm km\ s^{-1}}$ for CCSN & \confinv{268}{16}{17} & \confinv{92}{10}{9} & \confinv{143}{12}{12} & \confinv{34}{6}{5} & \confinv{427}{21}{21} & \confinv{143}{12}{12} & \confinv{229}{15}{15} & \confinv{55}{8}{7}\\
        R & Black holes receive not natal kick & \confinv{230}{15}{15} & \confinv{91}{10}{9} & \confinv{132}{11}{12} & \confinv{7}{2}{3} & \confinv{373}{20}{19} & \confinv{142}{12}{12} & \confinv{219}{15}{14} & \confinv{12}{4}{3}\\
        S & Wolf-Rayet wind factor $f_{\rm WR} = 0.1$ & \confinv{118}{10}{11} & \confinv{76}{9}{8} & \confinv{34}{6}{6} & \confinv{9}{3}{3} & \confinv{182}{13}{14} & \confinv{112}{10}{11} & \confinv{56}{8}{7} & \confinv{14}{4}{4}\\
        T & Wolf-Rayet wind factor $f_{\rm WR} = 5.0$ & \confinv{30}{6}{5} & \confinv{6}{3}{2} & \confinv{16}{4}{3} & \confinv{8}{2}{3} & \confinv{49}{7}{7} & \confinv{9}{3}{3} & \confinv{26}{5}{5} & \confinv{13}{3}{4}\\

@@

        - & Minimum rate & \confinv{30}{6}{5} & \confinv{6}{3}{2} & \confinv{2}{1}{2} & \confinv{0}{0}{1} & \confinv{49}{7}{7} & \confinv{9}{3}{3} & \confinv{3}{1}{2} & \confinv{0}{0}{1} \\
        - & Maximum rate & \confinv{321}{18}{18} & \confinv{154}{12}{13} & \confinv{148}{12}{13} & \confinv{35}{6}{6} & \confinv{484}{22}{22} & \confinv{240}{16}{15} & \confinv{229}{15}{15} & \confinv{57}{7}{8} \\
